---
output:
  revealjs::revealjs_presentation:
    self_contained: false
    reveal_plugins: ["notes", "search", "chalkboard", "menu"]
    
---

```{r child="page-definitions.Rmd"}
```
  
# {data-background-image="./images/title-slide.jpg"}


```{r child="additional-help.Rmd"}
```

# Computer Setup

```{r child="computer-setup.Rmd"}
```

# Workshop Files

```{r child="workshop-files.Rmd"}
```

# What is a Shiny app?

```{r child="shiny-apps.Rmd"}
```

# Project 0: Our First App

```{r child="project0-firstapp.Rmd"}
```

# Project 1: User Interface

```{r child="project1-ui.Rmd"}
```

# Project 2: Reactives

```{r child="project2-reactives.Rmd"}
```

# Project 3: Plotting a Data Frame

```{r child="project3-data-frame.Rmd"}
```

# {data-background-image="./images/title-slide.jpg"}


# Four Approaches to Styling Shiny

```{r child="four-approaches.Rmd"}
```

# Method 1: Accepting the Shiny Defaults

```{r child="method1-defaults.Rmd"}
```

# Method 2: Shiny Themes

```{r child="method2-themes.Rmd"}
```

# Method 3: Dashboards

```{r child="method3-dashboards.Rmd"}
```

# Method 4: Bootstraplib

```{r child="method4-bslib.Rmd"}
```

# Let's Make a Dashboard!

```{r child="dashboard.Rmd"}
```